Implementing Option Pricing Model

### 2019-12-19 draft.Rmd
Update draft.Rmd

---
title: "Implementing Option Pricing Modle"
author:
- affiliation: Utah State University
  name: Zhao Ming
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
  html_document:
    df_print: paged
  word_document: default
biblio-style: apsr
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
keywords: Monte Carlo, control variates, option pricing
bibliography: ./master.bib
spacing: double
abstract: 'In this paper I replicate Clewlow and Strickland’s control variates methods
  based on Greek letters method to test if it can improve the simulation efficiency.
  First, I use Black Scholes Merton formula for option pricing as a benchmark, to compare
  with the Euorpean call option price from Monte Carlo methods. Then I use Greek
  letters as control variates to reduce sample standard deviation and improve the
  efficiency of the Monte Carlo simulation. The whole process is programming in C++.
  C++ is a compiled language which can generate machine code from source code and
  provide a shorter running time. This paper is based on ideas from *Implementing
  Derivatives Models* by Clewlow and Strickland, *On The Simulation of Contingent
  Claims* by Clewlow and Carverhill, Chapter 4, and *Derivatives Markets*
  by McDonald, Chapter 12, 13, 19. '
---

>>>>

---
title: "Implementing Option Pricing Model"
author:
- affiliation: Utah State University
  name: Zhao Ming
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
  html_document:
    df_print: paged
  word_document: default
biblio-style: apsr
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
keywords: Monte Carlo, control variates, option pricing
bibliography: ./master.bib
spacing: double
abstract: 'In this paper I replicate Clewlow and Strickland’s control variates methods
  based on Greek letters method to test if it can improve the simulation efficiency.
  First, I use Black Scholes Merton formula for option pricing as a benchmark, to compare
  with the Euorpean call option price from Monte Carlo methods. Then I use Greek
  letters as control variates to reduce sample standard deviation and improve the
  efficiency of the Monte Carlo simulation. The whole process is programming in C++.
  C++ is a compiled language which can generate machine code from source code and
  provide a shorter running time. This paper is based on ideas from *Implementing
  Derivatives Models* by Clewlow and Strickland, *On The Simulation of Contingent
  Claims* by Clewlow and Carverhill, Chapter 4, and *Derivatives Markets*
  by McDonald, Chapter 12, 13, 19. '
---
